---
title: "index.Rmd"
output: html_document
date: '2022-08-13'
---

```{r setup, include=FALSE}
source("analysis.R")
```

## Introduction

Incarceration trends had always get people's attention. In this assignment, I analysis the incarceration trends from 1970 to 2018 in United States. The data is complex and difficult to analysis, so I focus mainly on AL. I analyzed three topics include **Total jail population changed by year.**, **Incarceration rate by race**, and **Incarceration rate by County**. When there is too much data, I use data from AL and year 2018 as example to study. I cited [Incarceration trends](https://github.com/vera-institute/incarceration-trends#documentation) which is a good source to learn the incarceration trends.

## Summary information 


```{r, echo=FALSE}
summary_info <- list()
summary_info$max_pop_year <- max_pop_year
summary_info$min_pop_year <- min_pop_year
summary_info$mean_female_15to64 <- mean_female_15to64
summary_info$mean_male_15to64 <- mean_male_15to64 
summary_info$max_pop_county <- max_pop_county
summary_info$difference <- difference
```

## Chart
### Line Chart

```{r, echo=FALSE}
plota
```

### Bar Chart
```{r, echo=FALSE}
plotb
```

### Map
```{r, echo=FALSE}
map
```